---
title: "Package demo"
author: "William Shih, Ricardo Simpao, Nilay Varshney, Luke Yee"
date: "3/20/2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here is an example of how our package functions run. For our data set, we are using a "SGEMM GPU kernel performance Data Set," which measures the running times of a matrix-matrix product, given different parameter combinations.

```{r load, message = FALSE, warning = FALSE}
library(devtools)
library(tidyverse)
library(STA141CFinal)
library(furrr)

set.seed(141)
dat = read_csv("sgemm_product.csv")
dat = dat[sample(241000, 1000),]
dat2 = dat[1:100,]
```

```{r linear regression with bootstrap, cache = TRUE}
#We specifiy a specific column set
y = dat$`Run1 (ms)`
x = dat[,1:(ncol(dat)-4)]

#linear model objects
fit = linear_reg_bs_C(x, y, s = 10, r = 1000)
```

# Linear Regression with blb
```{r, echo = FALSE, cache = TRUE}
(b0 = bench::mark(
  linear_reg_bs(x = x, y = y, s = 10, r = 1000),
  linear_reg_bs_par(x = x, y = y, s = 10, r = 1000),
 linear_reg_bs_C(x, y, s = 10, r = 1000),
  check = FALSE)
)

ggplot2::autoplot(b0)
```

# 95 % Confidence Interval for Variable Coefficients
```{r CI of coef, cache = TRUE}
coef_CI(fit, alpha = 0.05)

coef_CI_par(fit,alpha = 0.05)
coef_CI_C(fit,alpha = 0.05)


(b1 = bench::mark(
  coef_CI(fit, alpha = 0.05),
  coef_CI_par(fit,alpha = 0.05),
  coef_CI_C(fit, alpha = 0.05),
  check = FALSE)
)

ggplot2::autoplot(b1)
```

Notice that `coef_CI_par` offers better memory allocation than `coef_CI`.

# 95% Prediction Interval

```{r prediction interval, cache = TRUE}
plan(multiprocess, workers = 4)
PI(fit, dat2[1:3, 1:14], alpha = 0.05)
PI_par(fit, dat2[1:3, 1:14], alpha = 0.05)
PI_C(fit, dat2[1:3, 1:14], alpha = 0.05)

(b2 = bench::mark(
  PI(fit, dat2[1:3, 1:14], alpha = 0.05),
  PI_par(fit, dat2[1:3, 1:14], alpha = 0.05),
  PI_C(fit, dat2[1:3, 1:14], alpha = 0.05),
  check = FALSE)
)

ggplot2::autoplot(b2)
```

# 95 % Confindence Interval for Variance
```{r variance interval, cache = TRUE}
s2_CI(fit, alpha = 0.05)
s2_CI_par(fit, alpha = 0.05)
s2_CI_C(fit, alpha = 0.05)

(b3 = bench::mark(
  s2_CI(fit, alpha = 0.05),
  s2_CI_par(fit, alpha = 0.05),
  s2_CI_C(fit, alpha = 0.05),
  check = FALSE)
)

ggplot2::autoplot(b3)
```



Notice that `s2_CI_par` offers better memory allocation than `s2_CI`.



